PBMC_Donor

### 2019-06-10 PBMC.Rmd
double checked with primary files so this is all correct

```{r OG prep}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/exported")
og<-read.csv("OG_PBMC.csv")
og<-rename(og, Donor=Study.ID, TB=TB.Status, SM=Helminth.Status)%>%
    filter(Donor!="", Excluded!="EX")%>%
    select(Donor, TB, SM, Exp.Name, Viability, Cells.Vial, OG.Viability, OG.Cell.., Excluded, Exp.Name, Cheryl)

@@

```{r combine}
pbmc<-merge(ics, og, by=c("Donor", "TB", "SM"), all=TRUE)
names(pbmc)<-c("Donor", "TB" , "SM" , 
             "ICS_Exp.Name" , "ICS_Viability", "ICS_Cells.Vial", "ICS_Exluded",
             "OG_Exp.Name" , "PreOG_Viability" , "PreOG_Cells.Vial" , "PostOG_Viability" , "PostOG_Cells.Vial" , "OG_Excluded" , "Cheryl") 
```

@@

#Merge the two tables together and keep all observations since the yerkes donors won't be in the epi data
    DonorInfo<-merge(pbmc, QFT, by="Donor", all = TRUE)
#Manual Edits that may get deleted after Kenya script is finalized
    DonorInfo$TB[DonorInfo$Donor=="NK2183"]<-as.character("HC")
    DonorInfo$QFT[DonorInfo$Donor=="NK2323"]<-0.04
    DonorInfo$SM[DonorInfo$Donor=="NK2325"]<-as.character("Unknown")

@@

```{r, eval=FALSE}
#This was to pick the most robust responders for something else so Idk
library(dplyr)
mimosa<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/Clean/CD4_MIMOSA_Complete.csv")
HD<-filter(mimosa, grepl("HD", mimosa$Sample))%>%
    filter(Stim!="PMA")
HDscores<-aggregate(score~Donor, HD, FUN=sum)
HDkeep<-head(arrange(HDscores, score), 10)
#382 479 487 are BCG
HDremove<-HD$Donor[!(HD$Donor %in% HDkeep$Donor)]
CD4<-dplyr::filter(CD4, !(Donor %in% HDremove))
MFI<-dplyr::filter(MFI, !(Donor %in% HDremove))
Compass<-dplyr::filter(Compass, !(Donor %in% HDremove))
Donor<-dplyr::filter(Donor, !(Donor %in% HDremove))
```

>>>>

```{r OG prep}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/exported")
og<-read.csv("OG_PBMC.csv")
og<-dplyr::rename(og, Donor=Study.ID, TB=TB.Status, SM=Helminth.Status)%>%
    dplyr::filter(Donor!="", Excluded!="EX")%>%
    dplyr::select(Donor, TB, SM, Exp.Name, Viability, Cells.Vial, OG.Viability, OG.Cell..,
                  Excluded, Exp.Name, Cheryl)

@@

```{r combine}
pbmc<-merge(ics, og, by=c("Donor", "TB", "SM"), all=TRUE)
names(pbmc)<-c("Donor", "TB" , "SM" , 
             "ICS_Exp.Name" , "ICS_Viability", "ICS_Cells.Vial", "ICS_Excluded",
             "OG_Exp.Name" , "PreOG_Viability" , "PreOG_Cells.Vial" , "PostOG_Viability" , "PostOG_Cells.Vial" , "OG_Excluded" , "Cheryl") 
```

@@

#Merge the two tables together and keep all observations since the yerkes donors won't be in the epi data
    DonorInfo <- merge(pbmc, QFT, by="Donor", all = TRUE)
    DonorInfo$TB[DonorInfo$Donor=="NK2183"]<-as.character("HC")
    DonorInfo <- filter(DonorInfo, Donor!="NK2325")
    DonorInfo$SM[DonorInfo$Donor=="NK2384"]<-as.character("X")

@@

```{r, eval=FALSE}
#This was to pick the most robust responders for something else so Idk
library(dplyr)
mimosa<-read.csv("/Applications/Old Computer/Day Lab/Flow-Data/Clean/CD4_MIMOSA_Complete.csv")
HD<-filter(mimosa, grepl("HD", mimosa$Sample))%>%
    filter(Stim!="PMA")
HDscores<-aggregate(score~Donor, HD, FUN=sum)
HDkeep<-head(arrange(HDscores, score), 10)
#382 479 487 are BCG
HDremove<-HD$Donor[!(HD$Donor %in% HDkeep$Donor)]
```
